Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-05-25 manuscript.Rmd
Updated results section. Programming Pareto.

To identify the terms

it is relatively new and has
become part of social work terminology,

 that are common to the framework of
evidence-based practices (EBP).  This topic area was selected because it is a
more recent area of research relative to other social work topics (e.g., child
welfare and case management).

The final part of the study involved a topical analysis by using regular
expressions to identify articles using keywords based on different levels of
evidence.  We specified four sets of keywords relating to meta-analysis,
systematic reviews, randomized controlled trials, and quasi-experimental
studies.  We refer to these as _sets_ of keywords because we used a number of
different variations on the spelling and related terminology.  For example, RCT
involved a search specification that such as "randomized control trial,"
"randomized controlled trial," and "RCT".  The complete definitions of these
are provided in the index.

Figure 4 is a stacked line chart showing the number of each type of article
throughout the study timeframe.  This figure shows increased numbers of all
study types.  It is important to consider this growth relative to the overall
growth of the field of social work.  Thus, in Figure 5, we plotted the
proportion of each keyword class relative to the overall number of articles for
that given year.  This shows an increase -- albeit a small increase -- in the
proportion of journals, providing evidence of growth relative to the overall
field.  Slightly more than 1% of all articles published contained a phrase
equivalent to randomized control trial.

>>>>

In this analysis, we focused on four different _levels of evidence_:
Meta-analysis, systematic reviews, randomized controlled trials (RCTs), and
quasi-experimental designs.  To identify these key words in the article
abstracts, we created a set of regular expressions of common spellings and
synonyms for each type of evidence (see Appendix B).  Regular expressions, also
referred to as regex and regexp, are sequences of characters that define
specific patterns in text documents and work much like the _find_ functions
common to word processors.  The regular expressions used to define the _levels
of evidence_ are presented in Appendix B and the study's source code.

A stacked line chart was used to show absolute change in the number of
occurrences for each level of evidence in article abstracts.  The line chart
shows increased numbers of occurrences for each level of evidence, with the
greatest amount of growth starting in year 2008.  The presence of systematic
reviews and meta-analyses did not have a sustained presence in  the literature
until approximately 1995.  In fact, the first occurrence of the key word
_systematic review_ did not appear until 1997 (cite).

To show relative change, we plotted the proportion of overall articles
published that contained the target key words for each year.  In 1989, RCTs and
Quasi-experimental studies were observed in approximately 1/2% of published
articles.  By 2013, the percentage of RCTs tripled and the percentage of
quasi-experimental doubled.  Meta-analyses appeared in 1989 and grew to almost
1/2% by 2013.  Systematic reviews first appeared in 1997, then again in 2003,
and grew to approximately 1% in 2013.

**Pareto chart**
